COG-ED Manuscript

### 2021-08-25 06_Paper/COG-ED/Manuscript.Rmd
wrote more methods section

## Analysis
We conducted all analysis as described in Westbrook et al. [-@Westbrook2013].
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Declining performance was investigated by calculating an analysis of variance (ANOVA) with three linear contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another ANOVA with three linear contrasts was computed to compare the mean reaction time (RT) between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NTLX ratings, six ANOVAs were computed, one for each NTLX subscale, and each with six linear contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
An ANOVA with six linear contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Each ANOVA in the analysis was followed up by a Tukey's test.
To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
**MLM explanation goes here**

>>>>

## Analysis
We conducted all analysis as described in Westbrook et al. [-@Westbrook2013].
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Declining performance was investigated by calculating an analysis of variance (ANOVA) with three linear contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another ANOVA with three linear contrasts was computed to compare the mean reaction time (RT) between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NTLX ratings, six ANOVAs were computed, one for each NTLX subscale, and each with six linear contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
An ANOVA with six linear contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Each ANOVA in the analysis was followed up by a Tukey's test.
To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
**MLM explanation goes here**
The association of ED and NFC was done using three separate regressions.
One regression used the AUC of each participant's SVs to predict their NFC score.
The second regression additionally included the mean of the NTLX subscales' AUCs of each participant as a predictor.
And the last regression used the AUC of each participant's SV, the AUC of the NTLX mental load subscale, and the AUC of the NTLX effort subscale to predict each participant's NFC score.
